### 2024-10-30 paper/5-eval.tex
Minor fix

In \spectecp{} the call instruction in \cref{eq:bug-1} pushes a frame and
enters the function body \cref{eq:bug-2}.
When the \texttt{br} is executed, it pops the label and removes the input
instructions until the end in \cref{eq:bug-3}.
As a result, the frame is remained after the executing the call.
The problem is that the \texttt{end} express both the end of the block and the
function,

@@

The code above is simplified version of \spectecp{}.
According to the semantics defined in

>>>>

In \spectecp{} the call instruction in \cref{eq:bug-1} pushes a frame and
enters the function body \cref{eq:bug-2}.
When the \texttt{br} is executed, it pops the label and removes the input
instructions until the end in \cref{eq:bug-3}.
As a result, the frame is remained after the executing the call.
The problem is that the \texttt{br} should remove the end of the block but
should not remove the end of the function, but \texttt{end} express the end of
the block and the function at the same time.

% Fix
To fix the problem, semantics of \enteri is changed.
The sequence of contexts that is pushed in the AL algorithm is stored,
and when a block is entered, exiting label and returning from a function is
appended according to the sequence.

@@

The code above is simplified version of \spectecp{} of \texttt{call},
\texttt{br}, and \texttt{returning from a function}.
By using the semantics defined in \cref{ch:semantics}, the example 5.1 results in the same result with the \officialp{}; $call(\$brAndReturning)$ does nothing.
